%% start of file `cvBbp-English.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8,top=2cm]{geometry}
%\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage{import}
\renewcommand*{\namefont}{\fontsize{22}{26}\mdseries\upshape}
% personal data
\name{\textbf{Bruno Alejandro}}{\textbf{Bahamondes Pérez}}
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-15mm}

\section{Personal Information}

\begin{itemize}
\item{\textbf{Address}: Estación Central, Santiago, Región Metropolitana, Chile.}
\item{\textbf{Phone Number}: +56 9 9199 9324}
\item{\textbf{Email}: bahamondesbp@gmail.com}
\item{\textbf{Rut}: 19.208.517-9}
\item{\textbf{Date of birth}: 22/01/1996}
%\item{\textbf{Gender}: Male}
\item{\textbf{Linkedin}: \url{https://www.linkedin.com/in/bbahamondes/}}
\end{itemize}

%\section{Objective}
%\small{ Continue polishing and developing my skills. Interested on learning anything I do not yet know.  }

\section{Summary}
\small{Bilingual Analyst Programmer with over two years of experience in the area. I'm experienced in managing Hadoop environments, troubleshooting JVM issues, configuration and network issues. I'm familiar with both Hortonworks and Cloudera environments with varying degrees of expertise in the Hadoop components. I'm also experienced in scripting. Mostly self taught on Bash and Python}

\section{Work History}
\begin{itemize}
\item{\cventry{2019--Present}{Customer Operations Engineer}{Cloudera}{Chile}{}{Bilingual Technical Support for Data in motion services like Apache Nifi, YARN, Spark, Kafka, Nifi Registry and Minifi.}}
\vspace{3pt}
\item{\cventry{2018--2019}{Associate Technical Support Engineer}{Hortonworks}{Chile}{}{Gave bilingual technical support for Hadoop services including HDFS, Zookeeper, YARN, etc; managing customer expectations and critical situations.}}
\vspace{3pt}
\item{\cventry{2017--2018}{Software Developer}{Bprog LTDA}{Chile}{}{Had to meet with clients, talk with them and offer a solution that best solves their problem. Had to work under pressure to meet deadlines.}}
\end{itemize}

\section{Qualifications}

%\vspace{3pt}

\begin{itemize}
\item{\cventry{2019--Present}{Ingenieria Informatica}{Instituto Profesional DuocUC}{Chile}{}{}}
\item{\cventry{2015--2017}{Analista Programador Computacional }{Instituto Profesional DuocUC}{Chile}{}{}}
%\item{\cventry{2014--2015(Incomplete)}{Bachillerato en Humanidades }{Universidad Alberto Hurtado}{Chile}{}{}}
\end{itemize}

\section{Skills}
\begin{itemize}
\item \textbf{Hadoop Ecosystem}\\HDFS, MapReduce, YARN, Apache NiFi, Hive, Kafka, Zookeeper, Spark, Kerberos, JVM Troubleshooting.
\vspace{3pt}
\item \textbf{Languages} \\Fluent English. Native Spanish
\vspace{3pt}
\item \textbf{Programming Languages} \\Advanced knowledge on: C\#, Python. Notions on: Java.
\vspace{3pt}
\item \textbf{Database Languages} \\SQL, PL/SQL, Transact-SQL.
\vspace{3pt}
\item \textbf{Web Development Languages} \\Advanced knowledge on: PHP, Django, Jquery, JavaScript, \LaTeX.
%\vspace{3pt}
%\item \textbf{Strengths} \\Detail Oriented. Problem Solving. Analytical. Task-Oriented. Pressure tolerance. Troubleshooting. Customer Service
\end{itemize}
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `cvBbp-English.tex'.
